FoRTE baseline

### 2019-09-10 analysis/paper/paper.Rmd
Tweak Figure 3 results text

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4."
)
fig("pairs-time-averaged.png")
```

The crown model (closed vs. finite) had the strongest effect:
Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few individual simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

>>>>

```{r pairs-time, fig.cap = pairs_time_cap}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Each point indicates a single ensemble run with a different parameter combination.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4."
)
fig("pairs-time-averaged.png")
```

Model configuration affected the emergent relationship between net primary productivity and leaf area index (Figure 3).
The crown model (closed vs. finite) had the strongest effect:
Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Although many simulations matched _either_ the observed net primary productivity or the observed leaf area index, only a few individual runs matched _both_.
